\textls[-0]{\thetitle}

### 2023-03-02 introduction.tex
promise tool availability
CCS concepts and key words

There is a growing trend among programming languages researchers
to use proof assistants to mechanize meta\-theories.
%
However, the programmer runs into an old problem
in the new setting of proof engineering:
the Expression Problem (EP) \cite{wadler-ep}.

@@

\item We contribute a prototypical implementation of our language
mechanism as a Coq plugin (\cref{sec:coqimpl}). The plugin works by
compiling surface-language definitions into Coq modules parameterized by
explicit extensibility hooks.

>>>>

There is a growing trend among programming languages researchers
to use proof assistants to mechanize meta\-theories.
%
However, the programmer runs into an old problem
in the new setting of proof engineering:
the \emph{expression problem} (EP) \cite{wadler-ep}.

@@

\item We contribute a prototypical implementation of our language
mechanism as a Coq plugin (\cref{sec:coqimpl}),
available at \url{https://anonymized-link-to-code}.
The plugin works by
compiling surface-language definitions into Coq modules parameterized by
explicit extensibility hooks.
